---
title: "How to deal with missing values using tidyR package"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

### Load the packages

```{r}

library(tidyverse)
library(nycflights13)

```

### Load the data-set

```{r}

flights <- flights %>% rownames_to_column("ID") 

head(flights)


```

### Check the NA values in data set

```{r}

head(is.na(flights))

sum(is.na(flights))

```

### Check NA values in each column of data set

```{r}

sapply(flights,function(x) sum(is.na(x))) %>% view

```

### Select few rows of the data-set

```{r}

flights_new <- flights %>% select(tailnum,arr_delay,dep_delay,arr_time)%>%
  slice(c(20:30,472,478,616,755,13862,14667,14686,14856,1783,1785,11269:11273))%>%
  view
  
```

### Drop the rows with missing values

```{r}

flights_new[complete.cases(flights_new),] %>% view


```

### Drop rows with missing values - Columnwise

```{r}

flights_new %>% drop_na(dep_delay) %>% view

```

### replace missing values with some other value

```{r}

flights_new %>% replace_na(list(tailnum="NO DATA")) %>% view


```

### fill in the missing value with previous or next non missing value

```{r}

flights_new %>% fill(tailnum,.direction="up") %>% view

flights_new %>% fill(tailnum,.direction="up") %>% fill(arr_delay,.direction="down")%>% view

```

### Summary:

-   `complete.cases( )` function is used to drop the rows with missing values

-   `drop_na()` function is used to check the missing values in specific column

-   `replce_na()` function is used to replace the missing value with another values

-   `fill()` function imputes the missing value with previous or next non-missing value
