---
title: "nesting and unnesting data using nest() and unnest() function"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

## Load the package

```{r}

library(tidyverse)

```

## Load the data-set

```{r}
mtcars %>% view
```

## Visualize the data

```{r}

mtcars %>%
  ggplot(aes(x=wt,y=mpg))+
  geom_point(size=2)

```

## Fit the linear regression model

```{r}

model <- lm(mpg~wt,data=mtcars)
model
summary(model)

```

## tidy the model output

```{r}

broom::glance(model)

```

## create nested tibbles

```{r}

mtcars %>%
  group_by(cyl)%>%
  nest()%>%
  view

```

## Run linear model on each group variable

```{r}

mtcars %>%
  group_by(cyl)%>%
  nest()%>%
  mutate(model_fit = purrr::map(data,function(df) lm(mpg~wt,data=df)),model_output = purrr::map(model_fit,broom::glance))%>%
  unnest(model_output)
         
```

## Summary

We created a list using `nest()` function by grouping a data frame with some grouping variable. Each group value will have its separate list, we got 3 separate lists for 3 separate grouping values.

Each list has a tibble inside it.

We train the linear regression model on each list using `map()` function from `purrr` package. Using `map()` function, we could iterate `lm()` function on each tibble within a list.

We stored a model parameters in tidy format using `glance()` function from `broom` package

The model parameters are stored as a list, we used `unnest()` function to convert the list back into a tibble.

Finally, we got three separate model parameters for 3 separate groups using one elegant data pipeline.
