---
title: "seperate ( ) function from tidyR package"
output: html_document
date: "sys.Date()"
---

Separate a character column into multiple columns with a regular expression or numeric locations.

## Load the tidyverse package

```{r}

library(tidyverse)

```

## check mtcars data set

```{r}

head(mtcars) %>% view
rownames(mtcars)

```

## Convert rownames into column as part of data set

```{r}

new_mtcars <- mtcars %>%
  tibble::rownames_to_column("description") %>%
  view

```

## seperate out the car model name and car company name

```{r}

new_mtcars <- new_mtcars %>%
  separate_wider_delim(description," ",
                       names = c("OEM","car_model"),
                       too_many = "merge",
                       too_few = "align_start") %>%
  view
```

## use regular expressions to seperate the columns

```{r}

df <- tibble(var = c("race_1", "race_2", "age_bucket_1", "age_bucket_2"))%>%
view

df %>% separate_wider_regex(var, c(var1 = ".*", "_", 
                                   var2 = ".*")) %>%  
  view


```


## create dummy data

```{r}
product_sale <- tibble(product = c("product1","product2","product3","product4"),
                       Geography = c("AP/507130","BR/800001","GJ/360001","MH/400001"),
                       Sale=c(23,42,13,19))%>%
  view

```

## seperate column using position

```{r}


product_sale1 <- product_sale %>%
   separate_wider_position(Geography, c(State=2,1,pin_code= 6)) %>%
  view

```



## Summary:

`separate()` function seperates character column into multiple new columns. It uses three methods to seperate the character column:

`separate_wider_delim()` splits the column by delimiter

`separate_wider_regex()` splits by using regular expressions

`separete_wider_position()` splits at fixed widths

`separate()` function works only on character columns
